Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-08-28 analysis/paper/paper-doc.qmd
restore attribute image (redirection)

![(a) Stemmed point from Yongsandong site. with landmarks showing the attributes considered in this study and corresponding landmarks:\
ML: Maximum length, tip to bottom, perpendicular to the length axis 1- 7\
BL: Body length, tip to the closest wing, perpendicular to the length axis 1- 3 or 1-10 depending on the artifact\
TL: Tang length, the closest wing from the tip to bottom,perpendicular to the length axis 3 - 7 or 10-7 depending on the artifact\
SL: (Maximum) stem length, perpendicular to the length axis. Closer tang curve's middle point from the tip to the most distant point of the basal end 9-7 or 4-7 depending on the artifact\
MW: mid width, dimension from margin to margin at the mid-point of the length 2 - 11 axis, perpendicular to the width axis.\
TW: tang width, dimension between each wing, perpendicular to the width axis 3 - 10\
SW: stem width, width of the basal end of the point, 5mm above the end 5 - 8](images/ISKM%20talk%202021-cut.png){#fig-two width="221"}

@@

# CRediT authorship contribution statement
Gayoung Park: Conceptualization, Software, Validation, Formal analysis,  Methodology, Resources, Data curation,  Writing - original draft, Writing - Review & Editing, Visualization, Project administration.

>>>>

![(a) Stemmed point from Yongsandong site. with landmarks showing the attributes considered in this study and corresponding landmarks:\
ML: Maximum length, tip to bottom, perpendicular to the length axis 1- 7\
BL: Body length, tip to the closest wing, perpendicular to the length axis 1- 3 or 1-10 depending on the artifact\
TL: Tang length, the closest wing from the tip to bottom,perpendicular to the length axis 3 - 7 or 10-7 depending on the artifact\
SL: (Maximum) stem length, perpendicular to the length axis. Closer tang curve's middle point from the tip to the most distant point of the basal end 9-7 or 4-7 depending on the artifact\
MW: mid width, dimension from margin to margin at the mid-point of the length 2 - 11 axis, perpendicular to the width axis.\
TW: tang width, dimension between each wing, perpendicular to the width axis 3 - 10\
SW: stem width, width of the basal end of the point, 5mm above the end 5 - 8](images/ISKM%20talk%202021-cut.png){#fig-two width="212"}

@@

# CRediT authorship contribution statement

Gayoung Park: Conceptualization, Software, Validation, Formal analysis, Methodology, Resources, Data curation, Writing - original draft, Writing - Review & Editing, Visualization, Project administration.
